Using forecasting models for new book publishing

### 2015-08-09 paper.tex
nueva figura

Thus, in this study there are three main stages: 
\begin{itemize}
  \item  First, after the editorial company has provided the raw data, taken directly from its database, a selection variables process is carried out. In this stage, a SOM cluster method is used to analyze data, to eliminate unrelated variables and to select the best variables to be considered in the forecasted model. This task may help to identify leading indicators to be used by the forecasting methods in order to improve the accuracy of future forecasts.

@@

>>>>

\begin{figure}[!h] 
\begin{center}
\includegraphics{stages.eps} \\
\caption{\small{Three main stages in this research: data analysis, (2) forecasting methods testing, and (3) subjectively adjusting the obtained results.}}
\label{fig:stages}
\end{center}
\end{figure}

Thus, in this study there are three main stages (see Figure \ref{fig:stages} for details): 
\begin{itemize}
  \item  First, after the editorial company has provided the raw data, taken directly from its database, a selection variables process is carried out. In this stage, an expert sales manager, using the information obtained analyzing the SOM cluster method results, removes some unrelated variables and selects the best variables to be considered in the forecasted model. This task may help to identify leading indicators to be used by the forecasting methods in order to improve the accuracy of future forecasts.

@@

  %  
  %  El proceso que seguimos, resumido para el paper, es:
  %  
  %  [43 entradas] en 2013-01 vamos a tomar 
  %  	pb_noneg.csv para obtener pb_ventas.csv (es el pb_ventas.arff)
  %  	y hacer el SOM
  %  
  %  [13 entradas] en 2013-02-08 vamos a tomar 
  %  	controlado_reducido.csv.arff (197 líneas)
  %  	pbenero.csv.arff (5656 líneas)
  %  	y hacer el SOM
  %  
  %  [7 entradas; materia editorial] en 2013-02-25 vamos a tomar
  %  	pbRAWtrn.arff
  %  	pbRAWtst.arff
  %
